Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-31 manuscript/manuscript.tex
removing subsections in discussion

There does not appear to be a significant relationship produced over the span of four years between the variables for housing affordability

\subsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
access to resources and opportunities, which can significantly impact health outcomes. The stable trend 
in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape over the years prior to the 2020 pandemic.
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.
County 1's significant high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.

>>>>

The disparity in median income over the studied years, particularly the peak observed in 2020, 
signifies economic fluctuations. Notably, county 1 stands out with significantly higher income 
compared to other counties, indicating potential disparities in resource access and opportunities. 
This wealth gap implies potential repercussions on community health outcomes. The consistent trend in 
the percentage of income spent on rent underscores a persistent challenge for residents, especially 
noticeable in counties 1 and 5, indicating enduring economic pressure.

Rehospitalization rates demonstrate stability across counties and years leading up to 2020, suggesting 
a consistent healthcare landscape. Counties 8, 2, and 5 exhibiting higher food stamp usage point to economic 
challenges faced by residents in these regions. This trend aligns with housing affordability issues, 
indicating a correlation between financial stress and reliance on government assistance programs.

The notably high uninsured rate in county 1 raises concerns about healthcare accessibility, likely 
linked to economic factors impacting insurance affordability. Conversely, the lower uninsured rate in 
Year 3 (2019) signifies positive progress. Analyzing the policies or interventions implemented during 
this period could provide valuable insights for effective healthcare reforms, offering potential guidance 
for future initiatives.
